Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Clean up dynamic foil section a bit

Static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies dynamic loading. Furthermore, since the range of angle of attack
encountered by a rotating blade increases with decreasing tip speed ratio, the
blades commonly undergo dynamic stall for tip speed ratios at and below those of
maximum rotor torque\cite{Para2002}. We then must understand the effects of
Reynolds number on the dynamic stall process.

Dynamic effects on blade loading can be distinguished between attached and
separated conditions.

\todo[inline]{Find reference to describe $Re$ effects on dynamic foil behavior.}

Bousman showed that dynamic stall was insensitive to Reynolds number for $Re=1.0
\times 10^5$--$2.5 \times 10^5$ \cite{Bousman2000-evaluation}, Though Singleton
and Yeager Jr. state that Reynolds number effects on dynamics stall remains an
unsolved question \cite{Singleton2000}.

\todo[inline]{Bousman: explain in what type of system, with what type of foil
this was done.}
\todo[inline]{you took quite a few references out of this section...?}
\todo[inline]{additional data in helicopter literature?}

>>>>

Static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies dynamic loading. Furthermore, since the range of angle of attack
encountered by a rotating blade increases with decreasing tip speed ratio, the
blades commonly undergo dynamic stall for tip speed ratios at and below those of
maximum rotor torque \cite{Para2002}. We then must understand the effects of
Reynolds number on the dynamic stall process.

Bousman \cite{Bousman2000-evaluation} states that dynamic stall is relatively
insensitive to Reynolds number for $Re=1.0 \times 10^5$--$2.5 \times
10^5$---judging from measurements on a pitching VR-7 foil in a wind and water
tunnel---since the loading is dominated by vortex shedding. However, Singleton
and Yeager Jr. \cite{Singleton2000} state that Reynolds number effects on
dynamic stall remains an unsolved question.

\todo[inline]{additional data in helicopter literature?}
